### 2019-03-07 docs/notebooks/results.Rmd
update methods in results.ipynb / results.Rmd

## Methods
Alexnet training:  
• based on Poder 2017  
https://arxiv.org/pdf/1707.09775.pdf
• Stochastic gradient descent  
• Learning rate for fully-connected layers: 1e-20  
• 10 epochs (as in Poder 2017), and 400 epochs

>>>>

## Methods
Fine-tuning Alexnet and VGG16:
* based on Põder 2017: https://arxiv.org/pdf/1707.09775.pdf
* Stochastic gradient descent
* Base learning rate: 1e-20
* Rate for fully-connected layers: 0.0001
* epochs: [10 (as in Poder 2017), 50, 200, 400, 800]
